### 2016-06-16 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Added test matrix to hose stream report; fixed channel list spacing in gas burner report

A total of seven experiments were conducted to study the impact of different hose stream and nozzle movement patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~gpm, three used a combination nozzle attached directly to a 1.75~in handline to flow water at approximately 120~gpm (Fig.~\ref{fig:monitor+handline}), and one used both a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at approximately 180~gpm. Experiments that used a monitor to flow water always applied the stream in a fixed position and were focused on changing the location of water application in addition to the stream pattern. The experiments that used a combination nozzle attached directly to a 1.75~in handline to flow water focused on impact of the motion of the nozzle.

\begin{figure}[!ht]
	\minipage{3in}
	\begin{center}
		\includegraphics[width=2.9in]{../Figures/Pictures/monitor}
	\end{center} 
	\endminipage \hfill
	\minipage{3in}
	\begin{center}
		\includegraphics[width=2.9in]{../Figures/Pictures/handline}
	\end{center}
	\endminipage \hfill
	\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75~in handline (right) equipped with a combination nozzle and used to flow water during experiments.}
	\label{fig:monitor+handline}
\end{figure}
\FloatBarrier

Three different structure flow path configurations were used for the seven experiments. Tests~1 and 5 were conducted in the Single Story Structure and used the configuration shown in Fig.~\ref{fig:east_setup}. Test~1 used a monitor and combination nozzle to flow water, and Test~5 used a combination nozzle attached directly to a handline to flow water.

Two different flow path configurations were used for experiments conducted in the Two Story Structure. The main difference between the two flow paths was the position of the south side door on the first level. Tests~2 and 6 used a configuration with the door opened (Fig.~\ref{fig:flow_path_1}), while Tests~3, 4, and 7 used a configuration with the door closed (Fig.~\ref{fig:flow_path_2}). Tests~2 and 3 used a combination nozzle attached to a monitor to flow water; Tests~6 and 7 used a combination nozzle attached directly to a handline to flow water; and Test~4 used both a combination nozzle and a 1~in tip smooth bore nozzle attached to a monitor to flow water in a straight and solid stream, respectively.

@@

\subsection{Monitor Experiments}
\label{sec:monitor_procedure}
Three experiments, Tests~1--3, used a monitor equipped with a combination nozzle to flow water at 120~gpm in a straight stream, narrow fog stream, and wide fog stream. Test~1 occurred in the Single Story Structure, and Tests~2 and 3 occurred in the Two Story Structure. A fourth experiment, Test~4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively. The monitor was always set to flow water from a fixed position. Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure and provided a baseline to compare the impact of the motion of the nozzle on the air movement through the structure.

@@

\subsubsection{Test~4}
Test~4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests~2 and 3. The stairwell door was opened for the entire experiment. The test began by flowing water in a straight stream from a combination nozzle aimed at the near target. Then, the west double door on the second floor was opened. After 60 more seconds of flow, the nozzle was closed to stop water flow for 30 seconds. The nozzle was opened for 60 seconds and then closed for 30 seconds two additional times. Next, the monitor was aimed at the far target, and the procedure was repeated. This entire process was repeated for the solid stream from the smooth bore nozzle. Fig.~\ref{fig:test_4_pic} contains images of the straight stream from the combination nozzle and solid stream from the 1~in tip of the smooth bore nozzle during Test~4.

@@

\subsection{Handline Experiments}
\label{sec:handline_procedure}
Three experiments were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream. One test, Test~5, occurred in the Single Story Structure, and the remaining tests, Tests~6 and 7, occurred in the Two Story Structure. All three tests primarily focused on the impact of different hose stream and nozzle motion pattern selections on air movement in a structure.

@@

\subsubsection{Tests~6 \& 7}
Tests~6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room. The water stream was aimed at the south side wall of the first floor during the experiments. Test~6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test~7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each experiment began by using a straight stream to flow water in a fixed, horizontal position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth, left-to-right), clockwise, and counterclockwise nozzle motion patterns. This entire process was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test~6 with the flow path fully established.

@@

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lcccccccc}
\toprule
 &  & \multicolumn{7}{c}{\large ----------------------------- 120 gpm -----------------------------} 
\\
 &  & \underline{Test 1} &  & \multicolumn{2}{c}{\underline{Test 2}} &  & \multicolumn{2}{c}{\underline{Test 3}}
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}
\\ 
\midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   & -0.3 $\pm0.1$   & &  0.9 $\pm0.2$  &  0.9 $\pm0.2$  & &  0.7 $\pm0.1$  & 0.7 $\pm0.1$ \\ &
\small{(mph)} & (-0.7 $\pm0.1$) & & (2.0 $\pm0.4$) & (2.1 $\pm0.4$) & & (1.5 $\pm0.3$) & (1.5 $\pm0.3$) 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.1 $\pm0.2$  & &   1.0 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.8 $\pm0.1$ \\ &
\small{(mph)} &  (2.5 $\pm0.5$) & &  (2.1 $\pm0.4$) &  (3.2 $\pm0.6$) & &  (1.7 $\pm0.3$) & (1.7 $\pm0.3$) 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &  2.5 $\pm0.4$  & &   1.3 $\pm0.2$   &  1.4 $\pm0.2$   & &   1.2 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
\small{(mph)} & (5.6 $\pm1.0$) & &  (2.8 $\pm0.5$)  & (3.1 $\pm0.6$)  & & (2.7 $\pm0.5$) & (1.7 $\pm0.3$) 
\\ \midrule
 &  & \multicolumn{3}{c}{\large ------ 180 gpm ------} & \multicolumn{4}{c}{} 
\\
 &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &
 \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}} &
\multicolumn{4}{c}{} 
\\
\midrule
\multirow{2}{*}{\textit{Straight}} &
\small{m/s}   &   1.8 $\pm0.3$   & \multicolumn{2}{c}{2.0 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (3.9 $\pm0.7$) & \multicolumn{2}{c}{(4.4 $\pm0.8$)} & \multicolumn{4}{c}{} 
\\ \multicolumn{9}{c}{} \\
\multirow{2}{*}{\textit{Smooth Bore}} &
\small{m/s}   &   1.8 $\pm0.3$  &  \multicolumn{2}{c}{2.1 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (4.0 $\pm0.7$) & \multicolumn{2}{c}{(4.8 $\pm0.9$)} & \multicolumn{4}{c}{} 
\\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

@@

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for Test~5}
\begin{tabular}{lcccc}
\toprule
 &  & \multicolumn{3}{c}{\underline{Room A}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &   0.2 $\pm0.03$   &   0.7 $\pm0.1$  &   0.8 $\pm0.2$  \\ & 
\small{(mph)} &  (0.4 $\pm0.1$)   &  (1.5 $\pm0.3$) &  (1.9 $\pm0.3$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.7 $\pm0.3$   &   1.8 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
\small{(mph)} &  (3.9 $\pm0.7$)  &  (4.0 $\pm0.7$) &  (3.5 $\pm0.6$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   1.8 $\pm0.3$   &   2.1 $\pm0.4$  &   2.2 $\pm0.4$  \\ & 
\small{(mph)} &  (4.1 $\pm0.7$)  &  (4.8 $\pm0.9$) &  (4.9 $\pm0.9$)  
\\ \midrule
 & & \multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.1 $\pm0.02$    &  0.6 $\pm0.1$   &   0.5 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.2 $\pm0.04$)  &  (1.4 $\pm0.3$) &  (1.2 $\pm0.2$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   0.9 $\pm0.2$   &   1.5 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
\small{(mph)} &  (2.1 $\pm0.4$)  &  (3.4 $\pm0.6$) &  (3.7 $\pm0.7$)
\\ \multicolumn{5}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   2.1 $\pm0.4$   &   2.3 $\pm0.4$  &   2.6 $\pm0.5$  \\ & 
\small{(mph)} &  (4.7 $\pm0.8$)  &  (5.2 $\pm0.9$) &  (5.8 $\pm1.1$)  
\\ \bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

\begin{table}[!ht]
\caption{Average gas velocity [$\pm18$\%] through interior doorway when flow path was fully established for Tests~6 and 7}
\begin{tabular}{lccccc}
\toprule
 & & \multicolumn{4}{c}{\underline{Test 6}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.2 $\pm0.03$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.4 $\pm0.1$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.7 $\pm0.3$)
\\ \multicolumn{6}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   0.4 $\pm0.1$   &   1.1 $\pm0.2$  &   0.9 $\pm0.2$   &  1.1 $\pm0.2$  \\ & 
\small{(mph)} &  (0.9 $\pm0.2$)  &  (2.4 $\pm0.4$) &  (1.9 $\pm0.3$)  & (2.4 $\pm0.4$)
\\ \multicolumn{6}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   1.0 $\pm0.2$   &   1.0 $\pm0.2$  &   1.0 $\pm0.2$   &  0.9 $\pm0.2$  \\ & 
\small{(mph)} &  (2.2 $\pm0.4$)  &  (2.1 $\pm0.4$) &  (2.2 $\pm0.4$)  & (2.0 $\pm0.4$)
\\ \midrule
 & & \multicolumn{4}{c}{\underline{Test 7}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
\\ \multicolumn{6}{c}{} \\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
\\ \multicolumn{6}{c}{} \\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
\\ \bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}
\FloatBarrier

>>>>

A total of seven experimental series, summarized in Table~\ref{table:test_matrix}, were conducted to study the impact of different hose stream and nozzle motion patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~gpm, three used a combination nozzle attached directly to a 1.75~in handline to flow water at approximately 120~gpm (Fig.~\ref{fig:monitor+handline}), and one used both a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at approximately 180~gpm. Experiments that used a monitor to flow water always applied the stream in a fixed position and were focused on changing the location of water application in addition to the stream pattern. The experiments that used a combination nozzle attached directly to a 1.75~in handline to flow water focused on impact of the motion of the nozzle.

\begin{table}[!ht]
\caption{Summary of the seven experimental test series}
\begin{tabular}{ccclll}
 \toprule
\textbf{Test \#} & \textbf{Appliance} & \textbf{Structure} & 
\begin{tabular}{@{}l} \textbf{Flow Path} \\ \textbf{Configuration} \end{tabular} &
\textbf{Streams} & \textbf{Nozzle Motion} \\
\midrule
1 & Monitor & \begin{tabular}{@{}c@{}} Single \\ Story \end{tabular} & U-shaped & 
\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & 
Fixed position 
\\~\\
2 & Monitor & \begin{tabular}{@{}c@{}} Two \\ Story \end{tabular} & 
\begin{tabular}{@{}l} Nozzle lower \\ level north side, \\ Exhaust lower \\ level south side \\ and upper level \\ north side \end{tabular} & 
\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & Fixed position
\\~\\
3 & Monitor & \begin{tabular}{@{}c@{}} Two \\ Story \end{tabular} & 
\begin{tabular}{@{}l} Nozzle lower \\ level north side, \\ Exhaust upper \\ level north side \end{tabular} & 
\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & Fixed position
\\~\\
4 & Monitor & \begin{tabular}{@{}c@{}} Two \\ Story \end{tabular} & 
\begin{tabular}{@{}l} Nozzle lower \\ level north side, \\ Exhaust upper \\ level north side \end{tabular} & 
\begin{tabular}{@{}l} Straight, \\ Solid \\ (180~gpm) \end{tabular} & Fixed position
\\~\\
5 & Handline & \begin{tabular}{@{}c@{}} Single \\ Story \end{tabular} & U-shaped & 
\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & 
\begin{tabular}{@{}l} Fixed at ceiling, \\ Rotated CW, \\ Rotated CCW \end{tabular}
\\~\\
6 & Handline & \begin{tabular}{@{}c@{}} Two \\ Story \end{tabular} & 
\begin{tabular}{@{}l} Nozzle lower \\ level north side, \\ exhaust lower \\ level south side \\ and upper level \\ north side \end{tabular} & 
\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & 
\begin{tabular}{@{}l} Fixed at ceiling, \\ Sweeping ceiling, \\ Rotated CW, \\ Rotated CCW \end{tabular}
\\~\\
7 & Handline & \begin{tabular}{@{}c@{}} Two \\ Story \end{tabular} & 
\begin{tabular}{@{}l} Nozzle lower \\ level north side, \\ Exhaust upper \\ level north side \end{tabular} & 
\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & 
\begin{tabular}{@{}l} Fixed at ceiling, \\ Sweeping ceiling, \\ Rotated CW, \\ Rotated CCW \end{tabular} \\
\bottomrule
\end{tabular}
\label{table:test_matrix}
\end{table}

\begin{figure}[!ht]
	\minipage{3in}
	\begin{center}
		\includegraphics[width=2.9in]{../Figures/Pictures/monitor}
	\end{center} 
	\endminipage \hfill
	\minipage{3in}
	\begin{center}
		\includegraphics[width=2.9in]{../Figures/Pictures/handline}
	\end{center}
	\endminipage \hfill
	\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75~in handline (right) equipped with a combination nozzle and used to flow water during experiments.}
	\label{fig:monitor+handline}
\end{figure}

Three different structure flow path configurations were used for the seven experimental series. Tests~1 and 5 were conducted in the Single Story Structure and used a ``U-shaped'' configuration shown in Fig.~\ref{fig:east_setup}. Test~1 used a monitor and combination nozzle to flow water, and Test~5 used a combination nozzle attached directly to a handline to flow water.

Two different flow path configurations were used for the test series conducted in the Two Story Structure. The main difference between the two flow paths was the position of the south side door on the first level. Tests~2 and 6 used a configuration with the door opened (Fig.~\ref{fig:flow_path_1}), while Tests~3, 4, and 7 used a configuration with the door closed (Fig.~\ref{fig:flow_path_2}). Tests~2 and 3 used a combination nozzle attached to a monitor to flow water; Tests~6 and 7 used a combination nozzle attached directly to a handline to flow water; and Test~4 used both a combination nozzle and a 1~in tip smooth bore nozzle attached to a monitor to flow water in a straight and solid stream, respectively.

@@

\subsection{Monitor Experiments}
\label{sec:monitor_procedure}
Three experimental series, Tests~1--3, used a monitor equipped with a combination nozzle to flow water at 120~gpm in a straight stream, narrow fog stream, and wide fog stream. Test~1 occurred in the Single Story Structure, and Tests~2 and 3 occurred in the Two Story Structure. A fourth series, Test~4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively. The monitor was always set to flow water from a fixed position. Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure and provided a baseline to compare the impact of the motion of the nozzle on the air movement through the structure.

@@

\subsubsection{Test~4}
Test~4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests~2 and 3. The stairwell door was opened for the entire experimental series. The test began by flowing water in a straight stream from a combination nozzle aimed at the near target. Then, the west double door on the second floor was opened. After 60 more seconds of flow, the nozzle was closed to stop water flow for 30 seconds. The nozzle was opened for 60 seconds and then closed for 30 seconds two additional times. Next, the monitor was aimed at the far target, and the procedure was repeated. This entire process was repeated for the solid stream from the smooth bore nozzle. Fig.~\ref{fig:test_4_pic} contains images of the straight stream from the combination nozzle and solid stream from the 1~in tip of the smooth bore nozzle during Test~4.

@@

\subsection{Handline Experiments}
\label{sec:handline_procedure}
Three experimental series were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream. One series, Test~5, occurred in the Single Story Structure, and the remaining tests, Tests~6 and 7, occurred in the Two Story Structure. All three tests primarily focused on the impact of different hose stream and nozzle motion pattern selections on air movement in a structure.

@@

\subsubsection{Tests~6 \& 7}
Tests~6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room. The water stream was aimed at the south side wall of the first floor during the experiments. Test~6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test~7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each test began by using a straight stream to flow water in a fixed, horizontal position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth, left-to-right), clockwise, and counterclockwise nozzle motion patterns. This entire process was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test~6 with the flow path fully established.

@@

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
\begin{tabular}{lcccccccc}
\toprule
 &  & \multicolumn{7}{c}{\large ----------------------------- 120 gpm -----------------------------} 
\\
 &  & \underline{Test 1} &  & \multicolumn{2}{c}{\underline{Test 2}} &  & \multicolumn{2}{c}{\underline{Test 3}}
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &  &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}
\\ 
\midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   & -0.3 $\pm0.1$   & &  0.9 $\pm0.2$  &  0.9 $\pm0.2$  & &  0.7 $\pm0.1$  & 0.7 $\pm0.1$ \\ &
\small{(mph)} & (-0.7 $\pm0.1$) & & (2.0 $\pm0.4$) & (2.1 $\pm0.4$) & & (1.5 $\pm0.3$) & (1.5 $\pm0.3$) 
\\~\\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.1 $\pm0.2$  & &   1.0 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.8 $\pm0.1$ \\ &
\small{(mph)} &  (2.5 $\pm0.5$) & &  (2.1 $\pm0.4$) &  (3.2 $\pm0.6$) & &  (1.7 $\pm0.3$) & (1.7 $\pm0.3$) 
\\~\\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &  2.5 $\pm0.4$  & &   1.3 $\pm0.2$   &  1.4 $\pm0.2$   & &   1.2 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
\small{(mph)} & (5.6 $\pm1.0$) & &  (2.8 $\pm0.5$)  & (3.1 $\pm0.6$)  & & (2.7 $\pm0.5$) & (1.7 $\pm0.3$) 
\\ \midrule
 &  & \multicolumn{3}{c}{\large ------ 180 gpm ------} & \multicolumn{4}{c}{} 
\\
 &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
\\
\textbf{Stream} & \textbf{Units} &
\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &
 \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}} &
\multicolumn{4}{c}{} 
\\
\midrule
\multirow{2}{*}{\textit{Straight}} &
\small{m/s}   &   1.8 $\pm0.3$   & \multicolumn{2}{c}{2.0 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (3.9 $\pm0.7$) & \multicolumn{2}{c}{(4.4 $\pm0.8$)} & \multicolumn{4}{c}{} 
\\~\\
\multirow{2}{*}{\textit{Smooth Bore}} &
\small{m/s}   &   1.8 $\pm0.3$  &  \multicolumn{2}{c}{2.1 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
\small{(mph)} &  (4.0 $\pm0.7$) & \multicolumn{2}{c}{(4.8 $\pm0.9$)} & \multicolumn{4}{c}{} \\
\bottomrule
\end{tabular}
\label{table:all_mon_vel_avgs}
\end{table}

@@

\begin{table}[!ht]
\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for Test~5}
\begin{tabular}{lcccc}
\toprule
 &  & \multicolumn{3}{c}{\underline{Room A}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &   0.2 $\pm0.03$   &   0.7 $\pm0.1$  &   0.8 $\pm0.2$  \\ & 
\small{(mph)} &  (0.4 $\pm0.1$)   &  (1.5 $\pm0.3$) &  (1.9 $\pm0.3$)
\\~\\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   1.7 $\pm0.3$   &   1.8 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
\small{(mph)} &  (3.9 $\pm0.7$)  &  (4.0 $\pm0.7$) &  (3.5 $\pm0.6$)
\\~\\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   1.8 $\pm0.3$   &   2.1 $\pm0.4$  &   2.2 $\pm0.4$  \\ & 
\small{(mph)} &  (4.1 $\pm0.7$)  &  (4.8 $\pm0.9$) &  (4.9 $\pm0.9$)  
\\ \midrule
 & & \multicolumn{3}{c}{\underline{Room B Ceiling}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.1 $\pm0.02$    &  0.6 $\pm0.1$   &   0.5 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.2 $\pm0.04$)  &  (1.4 $\pm0.3$) &  (1.2 $\pm0.2$)
\\~\\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   0.9 $\pm0.2$   &   1.5 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
\small{(mph)} &  (2.1 $\pm0.4$)  &  (3.4 $\pm0.6$) &  (3.7 $\pm0.7$)
\\~\\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   2.1 $\pm0.4$   &   2.3 $\pm0.4$  &   2.6 $\pm0.5$  \\ & 
\small{(mph)} &  (4.7 $\pm0.8$)  &  (5.2 $\pm0.9$) &  (5.8 $\pm1.1$) \\ 
\bottomrule
\end{tabular}
\label{table:east_hand_A6_avgs}
\end{table}

\begin{table}[!ht]
\caption{Average gas velocity [$\pm18$\%] through interior doorway when flow path was fully established for Tests~6 and 7}
\begin{tabular}{lccccc}
\toprule
 & & \multicolumn{4}{c}{\underline{Test 6}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.2 $\pm0.03$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.4 $\pm0.1$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.7 $\pm0.3$)
\\~\\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &   0.4 $\pm0.1$   &   1.1 $\pm0.2$  &   0.9 $\pm0.2$   &  1.1 $\pm0.2$  \\ & 
\small{(mph)} &  (0.9 $\pm0.2$)  &  (2.4 $\pm0.4$) &  (1.9 $\pm0.3$)  & (2.4 $\pm0.4$)
\\~\\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &   1.0 $\pm0.2$   &   1.0 $\pm0.2$  &   1.0 $\pm0.2$   &  0.9 $\pm0.2$  \\ & 
\small{(mph)} &  (2.2 $\pm0.4$)  &  (2.1 $\pm0.4$) &  (2.2 $\pm0.4$)  & (2.0 $\pm0.4$) \\ 
\midrule
 & & \multicolumn{4}{c}{\underline{Test 7}}
\\
\textbf{Stream} & \textbf{Units} & 
\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\multirow{2}{*}{\textit{Straight}} & 
\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
\\~\\
\multirow{2}{*}{\textit{Narrow Fog}} & 
\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
\\~\\
\multirow{2}{*}{\textit{Wide Fog}} & 
\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$) \\ 
\bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}
\FloatBarrier
